Tracing R Base: +

### 2019-04-25 notebooks/corpus_stats_and_plots.Rmd
light modifications to some data files, new notebook, and new data

Plot:
```{r}
df_rc %>%
  mutate(rec=log10(rec),obs=log10(obs))  %>%
  ggplot(aes(y=rec, x=obs)) + geom_point(size=0.1) + 
    labs( x = "Observed", y = "Recorded") +
    scale_x_continuous(breaks = c( 1, 2, 3, 4, 5, 6, 7),
                       labels = c( 10, 100, 1000, 10000, 100000, 1000000, 10000000))+
    scale_y_continuous(breaks = c( 1, 2, 3, 4, 5, 6, 7),
                       labels = c( 10, 100, 1000, 10000, 100000, 1000000, 10000000))

>>>>

Plot:
```{r}
df_rc %>%
  mutate(rec=log10(rec),obs=log10(obs))  %>%
  ggplot(aes(y=rec, x=obs)) + geom_point(size=0.1) + 
    labs( x = "Calls Observed", y = "Signatures Recorded") +
    scale_x_continuous(breaks = c( 1, 2, 3, 4, 5, 6, 7),
                       labels = c( 10, 100, 1000, 10000, 100000, 1000000, 10000000))+
    scale_y_continuous(breaks = c( 1, 2, 3, 4, 5, 6, 7),
                       labels = c( 10, 100, 1000, 10000, 100000, 1000000, 10000000))

### 2019-04-25 notebooks/rplus.Rmd
light modifications to some data files, new notebook, and new data

# for L0
base_df_L0 <- transform_new_df_w_TS_map(base_df, type_map_T0_to_r, unparam = T)

@@

>>>>

# for L0
base_df_L0 <- transform_new_df_w_TS_map(base_df, type_map_T0_to_r, unparam = T)
base_df_L0 <- unlist_new_df(base_df_L0)

@@

```{r}
# pass things over to java
# dont forget to tar

# save L0
write_csv(base_df_L0, "../data/plus_80_L0.csv")
# save L1
write_csv(base_df, "../data/plus_80_L1.csv")

# do the java

# read subtype
subtype_df_L0 <- read_csv("../data/plus_80_L0_subtype.csv.gz")
subtype_df_L0 <- subtype_df_L0[!subtype_df_L0$pkg == "SUBTYPE",]
subtype_df_L1 <- read_csv("../data/plus_80_L1_subtype.csv.gz")
subtype_df_L1 <- subtype_df_L1[!subtype_df_L1$pkg == "SUBTYPE",]
subtype_df_L2 <- read_csv("../data/plus_80_L1_L2.csv.gz")
subtype_df_L2 <- subtype_df_L2[!subtype_df_L2$pkg == "SUBTYPE",]
```

```{r}
# just get +

subtype_df_L0_p <- filter(subtype_df_L0, fun == "+")
subtype_df_L1_p <- filter(subtype_df_L1, fun == "+")
subtype_df_L2_p <- filter(subtype_df_L2, fun == "+")

```
